PANCHANGE_analysis

### 2021-04-27 PANCHANGE_analysis.Rmd
new forest functions with adaptations ro C rayner for spacing

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(polycor)
library(corrplot)
library(patchwork)
library(broom)
library(tidyverse)
library(ggpubr)

@@

  ## Row labels
  independent.variables <- c("intercept",
                             "Comorbid depression and anxiety",
                             "Depressive disorders",
                             "Anxiety disorders",
                             "Eating disorders",
                             "Obsessive compulsive disorders",
                             "Comorbid psychotic and bipolar disorders",
                             "Psychotic disorders",
                             "Bipolar disorder",
                             "Post traumatic stress disorder",
                             "Autism spectrum disorder",
                             "Attention deficit hyperactivity disorder",
                             "Personality disorders",
                             "Female",
                             "Non-binary/Self-defined",
                             "16-18",
                             "19-25",
                             "36-45",
                             "46-55",
                             "56-65",
                             "66-70",
                             "71-75",
                             "76+",
                             "Mixed or multiple ethnicities",
                             "Asian",
                             "Black",
                             "Other",
                             "Key worker",
                             "Retired",
                             "Student",
                             "Unemployed",
                             "Time between lockdown and baseline")
  ## categories to facet on  
  categories <- c("Intercept",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Gender (Reference male)",
                  "Gender (Reference male)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Other")

@@

## Forest plots
### disorder
```{r forest plot by disorder prepan, fig.height=70, fig.width=55, dpi=120}

lm.forest(plot.dat.disorder.prepan,"Predictors of pandemic symptoms controlling for prepandemic symptoms")

```{r forest plot by disorder retro, fig.height=70, fig.width=55, dpi=120}

lm.forest(plot.dat.disorder.retro,"Predictors of pandemic symptoms controlling for retrospective symptoms")

>>>>

#Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(polycor)
library(corrplot)
library(patchwork)
library(broom)
library(tidyverse)
library(ggpubr)
library(cowplot)

@@

  ## Row labels
  independent.variables <- c("intercept",
                             "Comorbid depression and anxiety",
                             "Depressive disorders",
                             "Anxiety disorders",
                             "Eating disorders",
                             "Obsessive compulsive disorders",
                             "Comorbid psychotic and bipolar disorders",
                             "Psychotic disorders",
                             "Bipolar disorder",
                             "Post traumatic stress disorder",
                             "Autism spectrum disorder",
                             "Attention deficit hyperactivity disorder",
                             "Personality disorders",
                             "Female",
                             "Non-binary/Self-defined",
                             "16-18",
                             "19-25",
                             "36-45",
                             "46-55",
                             "56-65",
                             "66-70",
                             "71-75",
                             "76+",
                             "Mixed or multiple ethnicities",
                             "Asian",
                             "Black",
                             "Other",
                             "Key worker",
                             "Retired",
                             "Student",
                             "Unemployed",
                             "Time between lockdown and baseline")
  ## categories to facet on  
  categories <- c("Intercept",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Gender",
                  "Gender",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Ethnicity",
                  "Ethnicity",
                  "Ethnicity",
                  "Ethnicity",
                  "Employment",
                  "Employment",
                  "Employment",
                  "Employment",
                  "Other")

@@

## Forest plots

### palette

```{r palette for forest}

forestpal <- c("#993955","#2E5077","#E6C229")

```
### disorder
title: Predictors of pandemic symptoms controlling for prepandemic symptoms
```{r forest plot by disorder prepan, fig.height=70, fig.width=55, dpi=120}

plot_text_size=60

plot_grid(
  plot_grid(
    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Pre-existing mental health"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Gender"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Age"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Ethnicity"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Employment"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Other"), title="",colourpal=forestpal) +
      theme(
        axis.title.x = element_text(size = plot_text_size),
        axis.text.x = element_text(size = plot_text_size)),

    align = "v",
    nrow = 6,
    rel_heights = c(15/36, 2/36, 8/36, 4/36, 5/36, 2/36),
    hjust = c(0,0,0,0,0,0),
    vjust = c(2,0,0,0,0,0)
  ),
  as_ggplot(cowplot::get_legend(
    lm.forest(data %>% filter(Categories=="Other"), title="") +
      theme(legend.position = c(0.65,0.5),
            legend.direction = "horizontal",
            legend.box = "horizontal",
            legend.box.just = "centre",
            legend.title = element_blank(),
            legend.text = element_text(size = plot_text_size)) +
      guides(color = guide_legend(order = 1, reverse = T))
  )),
  ncol= 1,
  nrow = 2,
  rel_heights = c(1, 0.05)
)

Predictors of pandemic symptoms controlling for retrospective symptoms
```{r forest plot by disorder retro, fig.height=70, fig.width=55, dpi=120}

plot_grid(
  plot_grid(
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Preexisting mental health"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Gender"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Age"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Ethnicity"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Employment"), title="",colourpal=forestpal),
    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Other"), title="",colourpal=forestpal) +
      theme(
        axis.title.x = element_text(size = plot_text_size),
        axis.text.x = element_text(size = plot_text_size)),

    align = "v",
    nrow = 6,
    rel_heights = c(15/36, 2/36, 8/36, 4/36, 5/36, 2/36),
    hjust = c(0,0,0,0,0,0),
    vjust = c(2,0,0,0,0,0)
  ),
  as_ggplot(cowplot::get_legend(
    lm.forest(data %>% filter(Categories=="Other"), title="") +
      theme(legend.position = c(0.65,0.5),
            legend.direction = "horizontal",
            legend.box = "horizontal",
            legend.box.just = "centre",
            legend.title = element_blank(),
            legend.text = element_text(size = plot_text_size)) +
      guides(color = guide_legend(order = 1, reverse = T))
  )),
  ncol= 1,
  nrow = 2,
  rel_heights = c(1, 0.05)
)
